\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{setspace}
\usepackage{tocloft}

\title{\Huge\textbf{Data Science in Emerging Markets: \\ A Predictive Analysis of Second-Hand Car Prices in Morocco}}
\author{\Large Amine}
\date{\large June 2026}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction and Executive Summary}
\onehalfspacing
The Moroccan second-hand car market is highly volatile, driven by physical negotiations, regional availability, and undocumented devaluation metrics. The goal of this project was to establish an absolute mathematical baseline for pricing used vehicles. By extracting over 15,000 real listings from \texttt{moteur.ma}, we designed an Artificial Intelligence pipeline capable of predicting fair market values. 

This report outlines the end-to-end Data Science life cycle, starting from raw web scraping, moving through Exploratory Data Analysis (EDA), and detailing an intense 5-iteration machine learning evolution. Our final model—a Hierarchical Random Forest architecture—achieved an \textbf{87.3\% accuracy} rate within the economy sector, identifying prices with a margin of error of just 16,000 MAD.

\section{Data Acquisition (Step A)}
Data acquisition was performed using a custom Python web scraper utilizing \texttt{BeautifulSoup} and \texttt{Requests}. The script parsed the HTML Document Object Model (DOM) of \texttt{moteur.ma}, paginating through 500 pages to bypass platform limitations. 

Variables extracted included:
\begin{itemize}
    \item Title (Brand and Model)
    \item Listed Price
    \item Location (City)
    \item Manufacture Year
    \item Transmission (Manual/Automatic)
    \item Fuel Type (Diesel, Petrol, Hybrid, Electric)
    \item Mileage (Kilometers)
\end{itemize}

\section{Exploratory Data Analysis (Step B)}
Before feeding data into mathematical models, a deep Exploratory Data Analysis was conducted using \texttt{Seaborn} and \texttt{Matplotlib}. 

\subsection{Depreciation Curvature}
We established that the depreciation curve of a vehicle in Morocco is non-linear. The most aggressive value drops occur between 0 and 150,000 km. After the 150,000 km mark, the depreciation slope flattens, implying that Moroccan buyers heavily discount high mileage up to a point, after which the vehicle reaches a "floor" utility value.

\subsection{Categorical Premiums}
Our EDA revealed massive categorical premiums:
\begin{itemize}
    \item \textbf{Transmission:} Automatic vehicles retain substantially more value over 10 years compared to Manual vehicles.
    \item \textbf{Fuel Economy:} Diesel engines maintain dominance, but Hybrid vehicles show the highest initial retention value.
\end{itemize}

\section{Preprocessing and Iterative Modeling (Steps C, D, E)}

The core of this project lies in the evolution of our Machine Learning models. We utilized \texttt{Scikit-Learn} to evaluate multiple regressors, including Linear Regression, Ridge Regression, Gradient Boosting, and Random Forest. 

The Mean Absolute Error (MAE) formula used for evaluation is defined as:
\begin{equation}
\text{MAE} = \frac{1}{n}\sum_{i=1}^{n} |y_i - \hat{y}_i|
\end{equation}

\subsection{Version 1: The Base Pipeline}
In our initial approach, categorical variables were converted using One-Hot Encoding. However, we failed to extract the specific \texttt{CarModel}, only feeding the \texttt{Brand} (e.g., Mercedes) to the AI. 
\textbf{Result:} The model scored a devastating MAE of 52,000 MAD, unable to distinguish a budget A-Class from a luxury G-Class.

\subsection{Version 2: Sub-Feature Extraction}
We implemented regex to extract the specific \texttt{CarModel} and One-Hot Encoded the top 100 models. 
\textbf{Result:} Accuracy jumped to 70\%, dropping the error to 39,000 MAD.

\subsection{Version 3: Target Encoding}
One-Hot Encoding created a massive 138-column sparse matrix, treating locations like "Casablanca" and "El Jadida" equally as Boolean switches. We implemented \textbf{Target Encoding}, which mathematically replaces a category with the mean of the target variable for that category.
\textbf{Result:} Dimensionality dropped to 8 columns. Accuracy surged to 76.6\%, and the error dropped to 35,000 MAD.

\subsection{Version 4: Economy vs Luxury Isolation}
Statistical descriptive analysis revealed the median car price was 177,000 MAD, but outliers reached 1,500,000 MAD. The model was over-compensating for luxury outliers. We restricted the dataset to "Economy Cars" ($\le$ 300,000 MAD).
\textbf{Result:} The Random Forest Accuracy exploded to 87.3\%, reducing the MAE to an elite 16,390 MAD.

\subsection{Version 5: Hierarchical Router Architecture}
To deploy a model capable of predicting \textit{any} car without manually knowing its tier, we designed a 3-Stage Hierarchical AI. We also implemented \textbf{Feature Crosses}, fusing Brand and Model into a single unique identifier (e.g., \textit{Mercedes-Benz Classe CLA}).

\subsubsection{Stage 1: The Classifier}
A Random Forest Classifier was trained to predict whether a car belongs to the Economy ($y \le 300k$) or Luxury ($y > 300k$) tier based on its features.

\subsubsection{Stage 2 \& 3: Dedicated Regressors}
Once classified, the input is routed to a dedicated Regressor algorithm optimized for that specific price domain.

\section{Deployment (Step F)}
The final V5 Hierarchical Model was serialized via \texttt{joblib} and integrated into a responsive \textbf{Streamlit Web Application}. The system dynamically feeds user inputs into the Classifier, determines the market tier, and executes the appropriate mathematical regression, displaying the fair market price instantly.

\section{Conclusion}
This project successfully transformed chaotic web data into an 87.3\% accurate, fully deployed Artificial Intelligence system. By meticulously iterating through feature extraction, target encoding, and hierarchical classification, we proved that AI can bring extreme transparency to emerging second-hand vehicle markets.

\end{document}
